\chapter*{Acknowledgments}
\addcontentsline{toc}{chapter}{Acknowledgments}
\markboth{Acknowledgments}{Acknowledgments}

Upon the completion of this final year project, I would like to express my sincere gratitude to all those who contributed, directly or indirectly, to making this work possible.

First and foremost, I thank Allah for granting me the strength, perseverance, and clarity of mind needed to carry out this project.

I extend my deepest thanks to my professional tutor, \textbf{Mr.~Aabane Abderrahim}, for his attentive guidance, his willingness to help whenever I faced technical challenges, and his constant support throughout this internship experience. His expertise and availability were invaluable in overcoming the obstacles I encountered.

I am equally grateful to my manager, \textbf{Mr.~Couderc Pierre}, for his trust, his clear vision for the project's direction, and the autonomy he granted me while ensuring I always had the resources and support needed to move forward.

I sincerely thank my academic supervisor, \textbf{Pr.~El Bouzekri El Idrissi Younes}, for his rigorous follow-up, his constructive remarks, and the quality of his pedagogical guidance which helped structure this work according to academic standards.

I would also like to thank \textbf{Mrs.~Oumaira Ilhame} and \textbf{Mrs.~Ajanna Mehdia}, members of the jury, for the honor they bestow upon me by agreeing to examine and evaluate this work.

My heartfelt thanks go to the entire \textbf{Axelor Morocco} team for their warm welcome, their availability, and the collaborative environment they fostered. The exchanges and feedback I received from my colleagues greatly contributed to my professional growth during this period.

I also wish to acknowledge the entire faculty and administrative staff of the National School of Applied Sciences of Kénitra for the quality of education and training they provided throughout my academic journey.

Finally, I thank my family and friends for their unwavering support, encouragement, and patience throughout my studies. Their belief in me has been a constant source of motivation.
